\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-23 article.tex
Finished section on data, minor refactoring

% Method
%   Analysis of data || Processing
%    Difficulties related to tagging
%  Uncertainty
%
% Results
%   Tables
%   Graphs
% Conclusion

@@

% Set dimensions of columns, gap between columns, and paragraph indent
\setlength{\textheight}{8.875in}
\setlength{\textwidth}{6.875in}
\setlength{\columnsep}{0.3125in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\parindent}{1pc}
\setlength{\oddsidemargin}{-.1875in}  % Centers text
\setlength{\evensidemargin}{-.1875in}

@@

\begin{asydef}
// Global Asymptote definitions
import three;
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

\begin{document}

@@

\section*{\centering Abstract}
\begin{em}

@@

  \[
    \{1, 2, 3\} - \{2, 3, 4\} = \{1, 4\}
  \]

% why does this matter? how is it applied to tags and tagging?

@@

\SubSection{Approach}
% collecting data into text files
% tagging (how is tagging used? what is its role?)

  Todo.

% registered terminology to all pattern movements, grouped by pattern names, including their pattern movement number, and motion type (normal, slow, etc.), link to movements_all.txt ?
%   reviewed the terminology and movement type with odd-magne using a wiki
%   made a few changes (corrected terminology for punch for instance)
% added english description from the condensed encyclopedia to pattern
%   checked that the terminology corresponded to the actual pattern movement
% added tags
%   (documented the tagging process)
%   give an overview over (groups of) tags, see movements_with_tags.txt
% divided each pattern into its own text file
% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%
% show an example (chon-ji movement no. 1, for instance)
%
%
%
% The terminology to all pattern movements where first inserted into a text
% file, along with.. || including..
%

%   Tagging
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.

@@

% Observation: Kicks happen between stances

>>>>

@@

% Set dimensions of columns, gap between columns, and paragraph indent
\setlength{\textheight}{8.875in}
\setlength{\textwidth}{6.875in}
\setlength{\columnsep}{0.3125in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\parindent}{1pc}
\setlength{\oddsidemargin}{-.1875in}    % Centers the text
\setlength{\evensidemargin}{-.1875in}

@@

% Global Asymptote definitions
\begin{asydef}
import three;
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

% Document
\begin{document}

@@

% Sections
\section*{\centering Abstract}
\begin{em}

@@

  \[
    \{1, 2, 3\} \Delta \{2, 3, 4\} = \{1, 4\}
  \]

@@

  The terminology dataset is organized by pattern names. It contains a list of
  all techniques in patterns Chon-Ji to Juche using terminology. It also
  includes motion type on movements that are not performed in normal motion.
  The file was reviewed and minor corrections were made to the terminology.

\SubSection{Approach}

% the approach taken to register and investigate the dataset

% added English movement description from the condensed encyclopedia
% added tags
%   give an overview over (groups of) tags, see movements_with_tags.txt
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.
%   show an example (chon-ji movement no. 1, for instance)
% divided each pattern into its own text file (./patterns/*)
% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%

% Tagging
%   tagging (how is tagging used? what is its role?)
%   connect set theory to tagging? how is it applied to tags and tagging?

@@

% Observation: Kicks happen between stances
% Tables
% Graphs
